Yeast RNA-seq 48 sample simulation study

### 2018-02-15 datasets/RNA-Seq/yeast48-replicates-benchmarkFDR.Rmd
More flexibility to effectSize plotter - can also plot ind_covariate

plotEffectSize(de5)
plotEffectSize(de5, DE=FALSE)

@@

plotEffectSize(de10)
plotEffectSize(de10, DE=FALSE)

>>>>

plotEffectSize(de5, covname="log2FC")
plotEffectSize(de5, covname="log2FC", DE=FALSE)

plotEffectSize(de5, covname="ind_covariate")
plotEffectSize(de5, covname="ind_covariate", DE=FALSE)

@@

plotEffectSize(de10, covname="log2FC")
plotEffectSize(de10, covname="log2FC", DE=FALSE)

plotEffectSize(de10, covname="ind_covariate")
plotEffectSize(de10, covname="ind_covariate", DE=FALSE)
